Analyzing the impact of social attributes on the success of commit integration

### 2017-02-18 Paper/MSRChallenge2017.tex
rewrote the threats to validity and the conclusion

\noindent\textbf{Internal validity:}
The researchers in this study used the dataset provided by the 
MSRChallenge~\cite{msr17challenge} to gain useful information regarding the 
behavior of developers when pushing commits and how well these commits integrate 
successfully with the project. The authors have used 
Weka,\footnote{http://www.cs.waikato.ac.nz/ml/weka/} the well known tool for 
usage of machine learning algorithms to analyze our datasets. We are aware that, 
as every human written tool, Weka is prone to contain errors and/or bugs; 
nonetheless, Weka is a broadly used, open source tool that is subject to high 
quality standards and a vast user and developer base which makes it more likely 
to be a high quality code and to have less bugs than lesser used tools.

The scripts we have created to adapt and extract the datasets we needed, and the 
scripts to obtain the developer social data are publicly available to facilitate 
the transparency and quality of the process.\footnote{https://goo.gl/CqTX44}

\noindent\textbf{External validity:} 
External validity threats deal with the generalizability of our findings. 
To tackle the concern that the results of this study might not generalize to 
other instances outside of the studied cases, we have used a broad and rich 
dataset~\cite{msr17challenge} in our analysis that comprises 1,359 projects. The 
projects used in this dataset have also been filtered to be popular (having more 
than 10 watches on Github), and to have a history of using the continuous 
integration tool Travis CI for more than 50 builds. All these features help to 
build the notion that since we are building our analysis on top of a vast 
dataset comprehending a wide diversity of projects, the threat of this analysis 
not generalizing to other projects is mitigated.

\noindent\textbf{Construct validity:}
Regarding the suitability of our evaluation metrics, the authors understand that 
Travis job success is not the only way to analyze the success of a commit, and 
that for different reasons the job may not be successful even if the code 
commited does not have flaws (a flacky test case for example). Since continuous 
integration is a best known practice in industry and the use of this methodology 
spreads out into the open source community, we consider that cases of misuse of 
CI such that it will lead to failing travis jobs when they should have actually 
be successful are minimum, specially since having a solid build is one of the 
main purposes of the methodology, and taking into account that the projects in 
out dataset are projects with a history of using continuous integration and 
having a certain level of popularity, this threat is minimized. We therefore 
consider Travis job success to be a proxy 
for success when integrating a commit into a larger project.

\section{Conclusion}
In this study we have analyzed the probability of Travis job success as being predicted by two different categories of attributes: Technical and Social data.
We gathered the attributes that describe complexity of each commit being pushed and have created a decision tree that predicts if a future pushed commit will be successfully integrated into its corresponding build or not.
Afterwards, we have gathered social attributes from the developers who pushed each of these commits
and we have augmented our dataset with these attributes to understand whether adding social information about the developer would help the decision tree predict with higher accuracy future 
instances.

Our results show that adding social data to the construction of the decision tree increases the probability this correctly predicting future commit's success in integrating into their corresponding projects by a margin of 4.09\% to 11.99\%, depending on the ratio of successful vs unsuccessful instances are used to train the desicion tree.
\todo{maybe add here some other answers to smaller deduced RQ's}

>>>>

\noindent\textbf{Internal validity:}
One source of internal validity concern is the time mismatch between the
technical and social data.  We restricted the commits to only the commits in the
last three years of the data set to reduce this concern.
There is also a chance that scripts we used to create the data sets contain an
error.  For full transparency, we've released the scripts used to collect the
data set at (This will be added after the anonymous review).

%footnote{https://goo.gl/CqTX44}

\noindent\textbf{External validity:} 
While we have used a data set with high quality standards~\cite{msr17challenge},
these results may not generalized to non-open source projects.

\noindent\textbf{Construct validity:}
While we believe the build status is a good metric for contribution success,
there is the chance that a problem in the projects's test cases, and no the
contribution itself, led to the build failure.

\section{Conclusion}
In this study we have analyzed the ability to use social factors to predict
build integration success.
Our results show that adding social data, which proxies experience, provides a
small increases in prediction accuracy.  This leads us to conclude that while
experience is important, it is not the only factor in build success.
We have also found that non-core contributors cause not successful builds more
than core contributors.  This leads us to believe that non-core contributions
are not inspected as closely as they should be.
